Excuse me, do you have a moment to talk about version control?

### 2017-06-30 README.Rmd
Add link suggested by @nicholasjhorton; fixes #13

---
title: "Excuse me, do you have a moment to talk about version control?"
authors:
- name: Jennifer Bryan
  affiliation: |
    RStudio and the Department of Statistics, University of British Columbia
  thanks: |
    The author gratefully acknowledges the constructive feedback from reviewers
    Nicholas Horton, Colin Rundel, and Hadley Wickham.
blinded: 0
output:
  rticles::asa_article: null
  github_document:
    toc: yes
keywords: version control
abstract: Abstract abstract abstract.
bibliography: git-github-for-stats.bib
---

@@

Don't fret too much about public versus private repositories at this point. All the major hosting providers offer private repositories with flexible control over who can read or write to the repo. There are many ways to get private repositories for low or no cost, especially for academics. If you outgrow this initial arrangement, you can throw some combination of technical savvy and money at the problem. You can either pay for a higher level of service, self-host one of these platforms, or advocate for organization-wide solutions.

>>>>

---
title: "Excuse me, do you have a moment to talk about version control?"
authors:
- name: Jennifer Bryan
  affiliation: |
    RStudio and the Department of Statistics, University of British Columbia
  thanks: |
    The author gratefully acknowledges the constructive feedback from reviewers
    Nicholas Horton, Colin Rundel, and Hadley Wickham.
blinded: 0
output:
  github_document:
    toc: yes
  rticles::asa_article: null
keywords: version control
abstract: Abstract abstract abstract.
bibliography: git-github-for-stats.bib
---

@@

Don't fret too much about public versus private repositories at this point. All the major hosting providers offer private repositories with flexible control over who can read or write to the repo. There are many ways to get private repositories for low or no cost, [especially for academics](https://help.github.com/articles/discounted-organization-accounts/). If you outgrow this initial arrangement, you can throw some combination of technical savvy and money at the problem. You can either pay for a higher level of service, self-host one of these platforms, or advocate for organization-wide solutions.
